Nail: A practical interface generator for data formats

### 2014-09-09 paper/osdi14/eval.tex
whew, lots of bib crap

Duplicating information made sense when ZIP files were stored on floppy
disks with slow seek times and high fault rates, and memory constraints
made it impossible to keep the ZIP directory in memory or the archive
was split across multiple disks.  However, care must be taken that the
metadata is consistent. For example, vulnerabilities could occur if
the length in the central directory is used to allocate memory and the
length in the local directory is used to extract without checking that
they are equal first, as was the case in the Python ZIP
library~\cite{cve-2012-7338}.
\begin{comment}
\begin{figure}[tb]
\smaller[0.5]
\input{code/zip-eod-xform}
\caption{Signatures of stream transform functions for handling the
end-to-beginning structure of ZIP files.}
\label{fig:zip-eod-xform}
\end{figure}
\end{comment}
Figure~\ref{fig:zip-extract} shows an abbreviated version of our ZIP
file grammar.  The ZIP grammar is a good example of how transformations
capture complicated syntax in a real-world file format; existing parser
languages cannot handle a file format of this complexity.

>>>>

Duplicating information made sense when ZIP files were stored on floppy
disks with slow seek times and high fault rates, and memory constraints
made it impossible to keep the ZIP directory in memory or the archive
was split across multiple disks.  However, care must be taken that the
metadata is consistent. For example, vulnerabilities could occur if
the length in the central directory is used to allocate memory and the
length in the local directory is used to extract without checking that
they are equal first, as was the case in the Python ZIP
library~\cite{python-bug:20078}.
\begin{comment}
\begin{figure}[tb]
\smaller[0.5]
\input{code/zip-eod-xform}
\caption{Signatures of stream transform functions for handling the
end-to-beginning structure of ZIP files.}
\label{fig:zip-eod-xform}
\end{figure}
\end{comment}
Figure~\ref{fig:zip-extract} shows an abbreviated version of our ZIP
file grammar.  The ZIP grammar is a good example of how transformations
capture complicated syntax in a real-world file format; existing parser
languages cannot handle a file format of this complexity.

### 2014-09-09 paper/osdi14/intro.tex
whew, lots of bib crap

Third, many data formats contain redundancies, such as repeating
information in multiple structures.  Applications usually do not
explicitly check for consistency, and if different applications use
different instances of the same value, an attacker can craft input that
causes inconsistencies~\cite{evaders6}.  Furthermore, security
vulnerabilities can occur when an application assumes two repetitions
of the same data to be consistent, such as allocating a buffer based on
the value of one size field and copying into that buffer based on the
value of another~\cite{cve-2012-7338}.

>>>>

Third, many data formats contain redundancies, such as repeating
information in multiple structures.  Applications usually do not
explicitly check for consistency, and if different applications use
different instances of the same value, an attacker can craft input that
causes inconsistencies~\cite{evaders6}.  Furthermore, security
vulnerabilities can occur when an application assumes two repetitions
of the same data to be consistent, such as allocating a buffer based on
the value of one size field and copying into that buffer based on the
value of another~\cite{python-bug:20078}.
